\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
update bibtex

\subsection{Joint attention and social behaviour analysis}

@@

The task was performance-oriented and yet we were interested in accessing and
understanding the cognitive mechanisms at stake during the interaction: where do
the participant look when they want to understand a robot behaviour? Does
\emph{anticipation} reflect understanding? How the robot's design impact the
interaction?

>>>>

\subsection{Analysing social behaviour}

\begin{enumerate}
\item Joint attention
\item interaction episodes
\end{enumerate}

@@

The task was performance-oriented and yet we were interested in accessing and
understanding the cognitive mechanisms at stake during the interaction: where do participants look when they want to understand a robot behaviour? Does
\emph{anticipation} reflect understanding? How the robot's design impact the
interaction?
